Universal scaling for the ionization of biological molecules by highly charged ions

### 2020-05-11 zscaling/submitted/zscaling.tex
reviewers comments

\documentclass[10pt,showpacs,showkeys,twocolumn]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[T1]{fontspec}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{float}
\usepackage{MnSymbol}
\usepackage{gensymb}
\usepackage{comment}
\usepackage{wasysym} 
\usepackage{stmaryrd}

@@

Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM) to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}. The CDW--SSM approximation showed reasonable results for over a hundred of ion--molecule systems. As expected, in the high energy range (i.e. above 5 MeV/amu) the ionization cross sections  present the $Z^2$ dependence predicted by the first Born approximation. However, at intermediate energies, the dependence with $Z$ is more complex, and non--perturvative models are mandatory.

The intention of this letter is to give a follow up of our previous work~\cite{MendezJPB20} by proposing a scaling with the ion charge $Z$ of the ionization cross sections of complex molecules, valid at intermediate energies. In general, scaling rules are used as first--order tests in experimental measurements and multipurpose codes. Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.%, which is valid initially for the complex biological molecules studied here.

At intermediate impact energies, %the $Z^2$ rule no longer holds. 
Janev and Presnyakov~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of the ionization cross section $\sigma$ and the incident ion energy $E$. Much more recently, Montenegro and co--workers~\cite{dubois13,montenegro_pra13} proposed an alternative scaling by taking into account that  $\sigma$ is a function of $Z^2/E$. Their scaling, given by
\begin{equation}
    \sigma/Z^{\alpha}=f(E/Z^{2-\alpha}),
    \label{Montenegro}
\end{equation}
keeps the $Z^2/E$ relationship for any value of $\alpha$. 
In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization of He and H$_2$ by different charged ions.

\begin{figure*}[!t]%[h]
\centering
\includegraphics[width=0.7\textwidth]{zscale_alpha.eps}
\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function 
of ion impact energy $E/Z^{2-\alpha}$.%, given by Eq. (\ref{Montenegro}). 
%Colors are asociated with the impact charge as signed in the upper part of the figure. 
Colors are associated with the incident ion labeled on top of the figure.
Curves: present CDW--SSM theoretical results.
Symbols: experimental impact of 
\mbox{\Large$\circ$} H$^+$~\cite{iriki2011} and 
$\lozenge$ C$^{+6}$ \cite{tribedi2019} on adenine;
H$^+$ on  $\triangle$ uracil~\cite{itoh2013}, 
$\ominus$ C$^{+4}$, 
$\oplus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
$\otimes$ O$^{+8}$, F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
H$^+$ on $\triangledown$ pyrimidine~\cite{wolff2014}, and
$\meddiamond$ THF~\cite{wang2016};
\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007}, 
$\pentagon$ H$^+$ \cite{Rudd86}, 
$\odot$ He$^{+2}$ \cite{Rudd85},  
$\logof$ Li$^{+3}$ \cite{Luna_Li_water},  
$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
$\varobslash$ O$^{+8}$ \cite{Tribedi_O_water} on water.
Markers~$\square$~\cite{rahman2016}, 
$\rhd$~\cite{bug2017}, 
$\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} correspond to electron impact ionization with the equi-velocity conversion.}
\label{fig:zreduced}
\end{figure*}

% We consider our recent CDW-SSM results \cite{MendezJPB20} for eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$)eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$) as benchmark for the present scaling.

@@

%We found that $\sigma/Z^{\alpha}$ vs. $E^{2-\alpha}$, with $\alpha=1.2$ best fits the CDW-SSM scaled cross sections for all the ions. %$Z=+1$ to $+8$. , giving similar energy for the maximum of the cross sections. %, as displayed in  figure \ref{fig:zreduced}. 
We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
The validity of the theoretical scaling with the ion charge is very clear in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.  Our theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.

The scaling was tested with the experimental data available %for these eight molecules 
by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}. As can be noted, most of the data in Fig.~\ref{fig:zreduced} confirms the present scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}. However, the data of uracil by swift C, O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared with our CDW--SSM results, but also as compared with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
%as compared to proton impact measurements by Itoh \textit{et al} \cite{itoh2013} multiplied by $Z^2$. Independent CTMC calculations by Sarkadi \cite{sarkadi2016} also mention this. 
The data for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical curves for $E<600$ keV/amu.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Universal Scaling rule}
%\label{sec:U-scaling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule.  % that scales ions and molecules  
%Based on he good results shown in figure \ref{fig:zreduced}  and the scaling with the number of active electrons $n_e$ in each atom in  \cite{MendezJPB20}, we went further for an universal scaling that involves the different molecules biomolecules studied here, and 
To that end, we resorted to the %scaling with the 
number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}. %given by Eq. (\ref{Montenegro}) with $\alpha=1.2$.

The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O. %; and $4.5$ for P and S. 
The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.

\begin{table}[H]
\begin{center}
\begin{tabular}{|ll|ll|ll|}
\hline
 Molecule & $n_e$ &Molecule          & $n_e$ & Molecule             & $n_e$\\
\hline
% --------------------------------------------------------------------------------
% H$_2$    & 2  & CH$_5$N             \ \ \ \ & 13    & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -pyridine  -cytosine
% H$_2$O   & 6  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
% O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
% CH$_4$   & 8  & C$_6$H$_6$          \ \ \ \ & 30    & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-benzene-guanine
% CO$_2$   & 12 & C$_4$H$_4$N$_2$O$_2$\ \ \ \ & 36    & C$_5$H$_{10}$O$_5$P \ \ \ \ & 54.5 
% \\ %CO2- uracil-backbone
%--------------------------------------------------------------------------------
% Nueva tabla
% -------------------------------------------------------------------------------
 H$_2$O   & 6   &  CO$_2$  \ \ \ \ & 12  & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -CO2  -cytosine
 N$_2$    & 8  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
 O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
 CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ \ \ \ \ &  36   & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-uracil-guanine
% --------------------------------------------------------------------------------
 \hline
\end{tabular}
\caption{Number of active electrons per target at intermediate to high energies obtained from the CDW calculations~\cite{MendezJPB20}.}
\label{nn}
\end{center}
\end{table}

\begin{figure*}[!t]%[h]
\centering
\includegraphics[width=0.7\textwidth]{zmol_alpha.eps}
\caption{(Color online) Universal scaling with the ions charge $Z$ and the number of active electrons in the molecule $n_e$ given by Eq. (\ref{u-scaling}). Curves: present CDW-SSM theoretical results. 
Symbols: experimental impact of H$^+$ on 
\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
$\triangle$ uracil~\cite{itoh2013}, 
$\triangledown$ pyrimidine~\cite{wolff2014} and 
$\meddiamond$ THF~\cite{wang2016};
$\lozenge$ C$^{+6}$ on adenine \cite{tribedi2019};
\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007},
$\pentagon$ H$^+$ \cite{Rudd86}, 
$\odot$ He$^{+2}$ \cite{Rudd85},  
$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
$\boxslash$ O$^{+8}$ \cite{Tribedi_O_water} on water;
H$^{+}$ and He$^{+2}$ impact on 
$\boxast$~N$_2$, 
$\boxbox$~O$_2$,
$\boxbar$~CO, 
$\boxbslash$~CO$_2$, and
$\boxdot$~CH$_4$ \cite{Rudd85,Rudd1983}, 
$\varowedge$~H$^{+}$ on CH$_4$~\cite{Luna2019}; 
and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:zalpha}
\end{figure*}

The universal scaling we propose here is expressed as $\sigma_U$ as a function of $E/Z^{2-\alpha}$, with
 \begin{equation}
     \sigma_U=\frac{\sigma_e}{Z^{\alpha}}=\frac{\sigma/n_e}{Z^{\alpha}}\,,
     \label{u-scaling}
 \end{equation}
$\sigma$ is the ionization cross section for the molecular target, $\alpha=1.2$ and $n_e$ is the number of active electrons per molecule given in Table \ref{nn}. %It is important to point out that the scaling is based on CDW results atomic H, C, N, O, and P targets, so it is only  valid for ionization cross sections %by charged ions (at least up to +8) of molecules composed by these atoms.%, unless other values for ne were obtained for other atomic targets. 
In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq. (\ref{u-scaling}) %by showing in the same plot 
for all the theoretical and experimental values displayed in Fig. \ref{fig:zreduced}. 
As can be noted, the universal scaling works well, all the curves and data lays in a narrow band valid for any charged ion (scaling with Z) in any molecule (scaling with the number of active electrons). We decided not including in this figure the data for uracil from Ref.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water Ref.~\cite{Luna_Li_water}. The discussion about these experimental values exceeds the present work. %is open for future work.

@@

\bibitem{wang2016}
M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek, G. Hilgers, H. Rabus, 
Phys. Rev. A \textbf{93}, 052711 (2016).\bibitem{tribedi2019} S. Bhattacharjee, C. Bagdia, M. R. Chowdhury, A. Mandal, J. M. Monti, R. D. Rivarola, and L. C. Tribedi, 
Phys. Rev. A \textbf{100}, 012703(2019).

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen, H. Lekadir, P. F. Weck, and L. C. Tribedi. 
Phys. Rev. A \textbf{85}, 032711 (2012).

\bibitem{agnihotri2013}
A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
J. Phys. B: At. Mol. Opt. Phys.  \textbf{46}, 185201 (2013).

@@

%\bibitem{Champion2007}C. Champion, O. Boudrioua, C. Dal Cappello, Y. Sato, D. Ohsawa, Phys. Rev. A 75 (2007) 032724.

@@

% He$^{+2}$ in water---------------------
%\bibitem{DalCappello2007} O. Boudrioua, C. Champion, C. Dal Cappello, Y.V. Popov, Phys. Rev. A 75 (2007) 012717.

@@

% Li$^{+3}$ in water---------------------------
\bibitem{Luna_Li_water} H. Luna, W. Wolff, and E. C. Montenegro, Andre C. Tavares, H. J. Ludde, G. Schenk, M. Horbatsch, and T. Kirchner, Phys. Rev. A \textbf{93}, 052705 (2016).

% C$^{+6}$ in water--------------------------
\bibitem{DalCappello2009}
C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato , D. Ohsawa, 
Nuclear Instruments and Methods in Physics Research B 267 (2009) 781--790.

@@

\bibitem{sarkadi2016} L Sarkadi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)

>>>>

\documentclass[10pt,showpacs,showkeys,twocolumn]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[T1]{fontspec}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{float}
\usepackage{MnSymbol}
\usepackage{comment}
\usepackage{wasysym} 
\usepackage{stmaryrd}
\usepackage[outline]{contour}
\usepackage[dvipsnames]{xcolor}

\definecolor{olive}{RGB}{182,187,37}

@@

Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM), also known as the Bragg sum rule, to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}. The CDW--SSM approximation showed reasonable results for over a hundred of ion--molecule systems. As expected, in the high energy range (i.e. above 5 MeV/amu) the ionization cross sections  present the $Z^2$ dependence predicted by the first Born approximation. However, at intermediate energies, the dependence with $Z$ is more complex, and non--perturvative models are mandatory.

The intention of this letter is to give a follow up of our previous work~\cite{MendezJPB20} by proposing a scaling with the ion charge $Z$ of the ionization cross sections of complex molecules, valid at intermediate energies. In general, scaling rules are used as first--order tests in experimental measurements and multipurpose codes. Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.

At intermediate impact energies, 
Janev and Presnyakov~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of the ionization cross section $\sigma$ and the incident ion energy $E$. Much more recently, Montenegro and co--workers~\cite{dubois13,montenegro_pra13} proposed an alternative scaling by taking into account that  $\sigma$ is a function of $Z^2/E$. Their scaling, given by
\begin{equation}
    \sigma/Z^{\alpha}=f(E/Z^{2-\alpha}),
    \label{Montenegro}
\end{equation}
keeps the $Z^2/E$ relationship for any value of $\alpha$. 
In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization of He and H$_2$ by different charged ions.

\begin{figure*}[!t]%[h]
\centering
\includegraphics[width=0.7\textwidth]{zscale_alpha.eps}
\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function of ion impact energy $E/Z^{2-\alpha}$ with $\alpha=1.2$. Colors are associated with the incident ion labeled on top of the figure. Curves: present CDW--SSM theoretical results. Symbols: experimental impact of 
\mbox{\LARGE$\color{red}\circ$} H$^+$~\cite{iriki2011} and
{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ \cite{tribedi2019} on adenine;
H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
{\fontsize{11}{20}$\color{NavyBlue}\pmb{\ominus}$} C$^{+4}$, 
{\fontsize{11}{20}$\color{Purple}\pmb{\oplus}$} C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
{\fontsize{11}{20}$\color{BurntOrange}\pmb{\otimes}$} O$^{+8}$, F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} pyrimidine~\cite{wolff2014}, and
{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
% water
\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
O$^{+8}$ \cite{Tribedi_O_water} on water.
Markers~$\square$~\cite{rahman2016}, 
$\rhd$~\cite{bug2017}, 
$\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} correspond to electron impact ionization with the equi-velocity conversion.}
\label{fig:zreduced}
\end{figure*}

@@

We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
The validity of the theoretical scaling with the ion charge is very clear in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.  Our theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.

The scaling was tested with the experimental data available by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}. As can be noted, most of the data in Fig.~\ref{fig:zreduced} confirms the present scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}. However, the data of uracil by swift C, O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared with our CDW--SSM results, but also as compared with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
The data for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical curves for $E<600$ keV/amu.

The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule. 
To that end, we resorted to the number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}.

The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O, i.e.
\begin{equation}
 \frac{\sigma_{\mathrm{H}}^{\mathrm{CDW}}}{1}\sim
 \frac{\sigma_{\mathrm{C}}^{\mathrm{CDW}}}{4}\sim
 \frac{\sigma_{\mathrm{N}}^{\mathrm{CDW}}}{4}\sim
 \frac{\sigma_{\mathrm{O}}^{\mathrm{CDW}}}{4}
\end{equation}
The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.

\contourlength{0.03em}
\contournumber{30}

\begin{table}[H]
\begin{center}
\begin{tabular}{|ll|ll|ll|}
\hline
 Molecule & $n_e$ &Molecule          & $n_e$ & Molecule             & $n_e$\\
\hline
 H$_2$O   & 6   &  CO$_2$  \ \ \ \ & 12  & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ 
 N$_2$    & 8  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ 
 O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ 
 CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ \ \ \ \ &  36   & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ 
 \hline
\end{tabular}
\caption{Number of active electrons per target at intermediate to high energies obtained from the CDW calculations~\cite{MendezJPB20}.}
\label{nn}
\end{center}
\end{table}

\begin{figure*}[!t]%[h]
\centering
\includegraphics[width=0.7\textwidth]{zmol_werror.eps}
\caption{(Color online) Universal scaling with the ions charge $Z$ and the number of active electrons in the molecule $n_e$ given by Eq. (\ref{u-scaling}). Curves: present CDW-SSM theoretical results. 
Symbols: experimental impact of H$^+$ on 
\mbox{\LARGE$\color{red}\circ$} adenine~\cite{iriki2011}, 
{\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
{\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} pyrimidine~\cite{wolff2014} and 
{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ on adenine \cite{tribedi2019};
\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
O$^{+8}$ \cite{Tribedi_O_water} on water.
H$^{+}$ impact on 
{\fontsize{11}{20}${\color{red}\pmb{\boxast}}$}~N$_2$, 
{\fontsize{11}{20}${\color{red}\pmb{\boxbox}}$}~O$_2$, 
{\fontsize{11}{20}${\color{red}\pmb{\boxbar}}$}~CO, 
{\fontsize{11}{20}${\color{red}\pmb{\boxbslash}}$}~CO$_2$, and
{\fontsize{11}{20}${\color{red}\pmb{\boxdot}}$}~CH$_4$; 
and He$^{+2}$ impact on 
{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxast}}$}~N$_2$,
{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbox}}$}~O$_2$, 
{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbar}}$}~CO, 
{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbslash}}$}~CO$_2$, and
{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxdot}}$}~CH$_4$~\cite{Rudd85,Rudd1983}, 
{\fontsize{11}{20}${\color{red}\pmb{\varowedge}}$}~H$^{+}$ on CH$_4$~\cite{Luna2019}; 
and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:zalpha}
\end{figure*}

The universal scaling we propose here is expressed as $\sigma_U$ as a function of $E/Z^{2-\alpha}$, with
 \begin{equation}
     \sigma_U=\frac{\sigma_e}{Z^{\alpha}}=\frac{\sigma/n_e}{Z^{\alpha}}\,,
     \label{u-scaling}
 \end{equation}
$\sigma$ is the ionization cross section for the molecular target, $\alpha=1.2$ and $n_e$ is the number of active electrons per molecule given in Table \ref{nn}.
In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq. (\ref{u-scaling}) for all the theoretical and experimental values displayed in Fig. \ref{fig:zreduced}. We also included a gray area representing the 30\% deviation of our theoretical curves. As can be noted, the universal scaling works very well. All the curves and data lays in a narrow band valid for any charged ion (scaled with Z) in any molecule (scaled with the number of active electrons). 
We decided not to include in this figure the data for uracil from Refs.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water~\cite{Luna_Li_water}. The discussion about these experimental values exceeds the present work. %is open for future work.

@@

\bibitem{wang2016}
M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek,
G. Hilgers, H. Rabus, 
Phys. Rev. A \textbf{93}, 052711 (2016).

\bibitem{tribedi2019} 
S. Bhattacharjee, C. Bagdia, M. R. Chowdhury, A. Mandal, J. M. Monti, 
R. D. Rivarola, and L. C. Tribedi, 
Phys. Rev. A \textbf{100}, 012703(2019).

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A. Kumar, M. E. Galassi, 
R. D. Rivarola, O. Foj\'on, C. Champion, J. Hanssen, H. Lekadir, 
P. F. Weck, and L. C. Tribedi. 
Phys. Rev. A \textbf{85}, 032711 (2012).

\bibitem{agnihotri2013}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A. Kumar, C. Champion, 
H. Lekadir, J. Hanssen, P. F. Weck, M. E. Galassi, R. D. Rivarola, O. Foj\'on and 
L. C. Tribedi, 
J. Phys. B: At. Mol. Opt. Phys. \textbf{46}, 185201 (2013).

@@

@@

\bibitem{pRudd85} 
M. E. Rudd, T. V. Goffe, R. D. DuBois, L. H. Toburen, 
Phys. Rev. A \textbf{31}, 492 (1985).

\bibitem{toburen80} 
L. H. Toburen, W. E. Wilson and R. J. Popowich,
Radiat. Res. \textbf{82}, 27--44 (1980).

% He$^{+2}$ in water---------------------
\bibitem{Ohsawa05}
D. Ohsawa, Y. Sato, Y. Okada, V. P. Shevelko, and F. Soga
Phys. Rev. A \textbf{72}, 062710 (2005).

@@

% Li$^{+3}$ in water---------------------------
\bibitem{Luna_Li_water} 
H. Luna, W. Wolff, E. C. Montenegro, Andre C. Tavares, H. J. Ludde, 
G. Schenk, M. Horbatsch, and T. Kirchner, 
Phys. Rev. A \textbf{93}, 052705 (2016).

% C$^{+6}$ in water--------------------------
\bibitem{DalCappello2009}
C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato, D. Ohsawa, 
Nuclear Instruments and Methods in Physics Research B 267 (2009) 781--790.

\bibitem{Bhattacharjee17}
Shamik Bhattacharjee, S. Biswas, J. M. Monti, R. D. Rivarola, and L. C. Tribedi,
Phys. Rev A \textbf{96}, 052707 (2017).

@@

\bibitem{sarkadi2016}
L. Sarkadi, 
J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
